Improved Bounds for Online Balanced Repartitioning

### 2020-03-28 paper/paper.tex
LB

\newcommand{\OPT}{\textsf{OPT}\xspace}
\newcommand{\ALG}{\textsf{ALG}\xspace}
\newcommand{\PPL}{\textsf{PPL}\xspace}
\newcommand{\OBRP}{BRP}
\newcommand{\PPOBRP}{PP-BRP}
\newcommand{\dist}{\textsf{dist}}
\newcommand{\TAlg}{{\ensuremath{\textsf{ALG}_{3}}}\xspace} % we should change this name

@@

>>>>

\newcommand{\OPT}{\textsf{OPT}\xspace}
\newcommand{\ALG}{\textsf{ALG}\xspace}
\newcommand{\PPL}{\textsf{PPL}\xspace}
\newcommand{\OBRP}{BRP}
\newcommand{\PPOBRP}{PP-BRP}
\newcommand{\dist}{\textsf{dist}}
\newcommand{\TAlg}{{\ensuremath{\textsf{ALG}_{3}}}\xspace}

\newcommand{\comm}{\textsc{comm}}

@@

When a request $p$ to paging arrives, we create a subsequence $\comm(p)$ of communication requests for the BRP problem.
We identify the corresponding caching node $p$ and the set $S \in \{ A,B,C \}$ that contains it.
The construction of $\comm(p)$ depends on the actions of $B$.
To abstract from the actions of $B$ in the construction, we use the notion of the adversary components.
Forming an adversary component means that the adversary continuously issues requests to any two nodes of a component that are split.
The request sequence $\comm(p)$ consists of the requests the adversary issues for $B$ after forming an adversary component $S$.
When $B$ collocates all nodes of $S$, the adversary dismisses the adversary component $S$, i.e., no longer issues requests if $B$ splits the nodes of $S$.

Note that $B$ must eventually achieve such a node configuration: otherwise its cost would be arbitrarily large while a sequence of repeated $\comm(\sigma^P_t)$ subsequences can be served at~a~constant cost.
Therefore, the competitive ratio of~$B$ would then be unbounded.
We denote the resulting sequence of $\comm(\sigma^P_t)$ subsequences by $\comm_t(\sigma^P_t)$.
